Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-12 paper2_JNLS/paper.tex
NM

	We note that, in the current formulation, a positive inverse temperature $\invtemp > 0$ produces physically realistic statistics with a decaying energy spectrum, as is consistent with experiments \cite{majda2019, bajars2013weakly}. Negative inverse temperature produces a physically unrealistic spectrum that has more energy at smaller scales. Hence, we will hereafter focus on the physically realistic case of $\invtemp > 0$.

@@

	With these locations selected, we evaluate the ratio $\skw(\eta) / \Delta \var(\eta_x)$ for each experiment and plot the result against dimensionless wave amplitude, $\epsup = \etastd / \dup$ on a log-log scale in Fig.~\ref{SkewRat}(c). While the data shows significant variation at small amplitudes, it shows a well defined decreasing trend at larger amplitudes. In particular, the red dashed line shows the power-law $\epsup^{-3}$ predicted by \eqref{SkewPred}, which captures the experimental trend \new{closely}.

	\new{We remark that Eq.~\eqref{SkewPred} bears similarity to a formula derived by Onorato \& Suret \cite{onorato2016twenty}, in the context of {\em constant-depth} KdV, that relates variations in skewness to variations in spectral bandwidth. Indeed, since $\eta_t \approx c \eta_x$ to leading order, the term $\var(\eta_x)$ in Eq.~\eqref{SkewPred} could be (approximately) interpreted as the spectral bandwidth.
We note that an analogous formula has been derived for the nonlinear Schr{\"o}dinger equation relating kurtosis to bandwidth variations \cite{onorato2016origin}. The present study differs in that it predicts a moment-bandwidth relation for waves propagating over {\em variable} depth, where it is the depth change that creates system disequilibrium. A small transition region connects two near-equilibrium systems, i.e. one far upstream and one far downstream. The link between these two equilibrium states is made mathematically precise by the statistical matching condition \eqref{statmatch}, which is the key ingredient needed to derive Eq.~\eqref{SkewPred}. This is in contrast to the simpler situation of waves propagating over constant depth, where spectral variations and the associated moment variations arise from out-of-equilibrium initial conditions \cite{onorato2016twenty, onorato2016origin}.}

>>>>

	We note that, in the current formulation, a positive inverse temperature $\invtemp > 0$ produces physically realistic statistics with a decaying energy spectrum, as is consistent with experiments \cite{majda2019, bajars2013weakly}. Negative inverse temperature produces a physically unrealistic spectrum that has more energy at smaller scales. Hence, we will hereafter focus on the physically realistic case of $\invtemp > 0$. \new{We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.}

@@

	With these locations selected, we evaluate the ratio $\skw(\eta) / \Delta \var(\eta_x)$ for each experiment and plot the result against dimensionless wave amplitude, $\epsup = \etastd / \dup$ on a log-log scale in Fig.~\ref{SkewRat}(c). While the data shows significant variation at small amplitudes, it shows a well defined decreasing trend at larger amplitudes. \new{In particular, the decay rate of the ratio, $\skw(\eta) / \Delta \var(\eta_x) \sim \epsup^{-3}$, is well predicted by the explicit formula \eqref{SkewPred}, shown by the red dashed line in Fig.~\ref{SkewRat}(c).
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.}

	\new{We remark that Eq.~\eqref{SkewPred} bears similarity to a formula derived by Onorato \& Suret \cite{onorato2016twenty}, in the context of {\em constant-depth} KdV, that relates variations in skewness to variations in spectral bandwidth. Indeed, since $\eta_t \approx c \eta_x$ to leading order, the term $\var(\eta_x)$ in Eq.~\eqref{SkewPred} could be interpreted as approximately the spectral bandwidth.
We note that an analogous formula has been derived for the nonlinear Schr{\"o}dinger equation relating kurtosis to bandwidth variations \cite{onorato2016origin}. The present study differs in that it predicts a moment-bandwidth relation for waves propagating over {\em variable} depth, where it is the depth change that creates system disequilibrium. A small transition region connects two near-equilibrium systems, i.e. one far upstream and one far downstream. The link between these two equilibrium states is made mathematically precise by the statistical matching condition \eqref{statmatch}, which is the key ingredient needed to derive Eq.~\eqref{SkewPred}. This is in contrast to the simpler situation of waves propagating over constant depth, where spectral variations and the associated moment variations arise from out-of-equilibrium initial conditions \cite{onorato2016twenty, onorato2016origin}.}
